% \documentclass{article}
\documentclass[../../outputs/main.tex]{subfiles}

\usepackage{cite} % default

\usepackage{amsmath,amssymb,amsfonts} % default
\usepackage{cleveref}
% The following formats are used so that when I call \cref{label_1} or \cref{label_1,label_2} or \crefrange{label_1}{label_4}: 
    % 1. I never get eq. or eqs. before my bracketed numbers.
    % 2. The numbers are bracketed.

% For single equation references
\crefformat{equation}{(#2#1#3)}
\Crefformat{equation}{(#2#1#3)}
% For multiple equation references
\crefmultiformat{equation}
{(#2#1#3)} % First reference
{ and (#2#1#3)} % Middle references
{ and (#2#1#3)} % Last reference
{ and (#2#1#3)} % Last reference
% For a range of equation references (e.g., (1)-(3))
\crefrangeformat{equation}{(#3#1#4) to (#5#2#6)}


\usepackage{algorithmic} % default
\usepackage{graphicx} % default

% \usepackage[subpreambles=true]{standalone}
\usepackage{import}

% \usepackage{lipsum} 
\usepackage{textcomp} % default
\usepackage{xcolor} % default
% Any packages or configurations specific to this section
\usepackage{lipsum}

\begin{document}

\section{Problem Formulation}

\subsection{Notations}
In this study, the distribution network is accounted as a tree (connected graph) having $N$ number of buses (indexed with \(i\), \(j\), and \(k\)) and the study is conducted for $T$ time steps (indexed by $t$), each of interval length $\Delta t$. The sets of buses with DERs and batteries are $D$ and $B$ respectively, such that $D, B \subseteq N$.
A directed edge from bus $i$ to $j$ in the tree is represented by $ij$ and the set for edges is $\mathcal{L}$. Line resistance and reactance are \(r_{ij}\) ohm and \(x_{ij}\) ohm, respectively. Magnitude of the current flowing through the line at time \(t\) is denoted by \(I_{ij}^t\) and  $l_{ij}^t=\left(I_{ij}^t\right)^2$. The voltage magnitude of bus \(j\) at time \(t\) is given by \(V_j^t\) and  $v_j^t=\left(V_j^t\right)^2$. Apparent power demand at a node \(j\) at time \(t\) is \(s^t_{L_j}\) (\(=p^t_{L_j}+\textit{j}q^t_{L_j}\)). The active power generation from the DER present at bus \(j\) at time \(t\) is denoted by \(p^t_{D_j}\) and controlled reactive power dispatch from the DER inverter is \(q^t_{D_j}\). DER inverter capacity is $S_{D_{R_j}}$.
% Static capacitance attached to a node $j$ is denoted by $q_{C_j}$. 
The apparent power flow through line {\(ij\)} at time \(t\) is \(S_{ij}^t\) (\(=P_{ij}^t+\textit{j}Q_{ij}^t\)). The real power flowing from the substation into the network is denoted by $P^t_{Subs}$ and the associated cost involved per kWh is $C^t$. The battery energy level is \(B_j^t\). Charging and discharging active power from battery inverter (of apparent power capacity $S^{t}_{R_j}$) are denoted by \(P_{c_j}^t\) and \(P_{d_j}^t\), respectively and their associated efficiencies are $\eta_c$ and $\eta_d$ respectively. The energy capacity of the batteries is denoted by $B_{R_j}$, and the rated battery power is $P_{B_{R_j}}$. $soc_{min}$ and $soc_{max}$ are fractional values for denoting safe soc limits of a battery about its rated soc capacity. The reactive power support of the battery inverter is \(q_{B_j}^t\). 
% Rated apparent powers of DERs and Batteries at node $j$ are denoted by $S_{D_{R_j}}$ and $S_{B_{R_j}}$ respectively.

\subsection{MPCOPF with Batteries}
The OPF problem aims to minimize two objectives 
 as shown in \cref{eq:genCost_withSCD}. The first term in \cref{eq:genCost_withSCD} aims to minimize the total energy cost for the entire horizon. The incorporation of 'Battery Loss' cost as the second term ($\alpha > 0$) helps to avoid the usage of binary (integer) variables generally used to refrain from simultaneous charging/discharging. This is done to make the OPF problem a simple non-convex problem but not a MINCP. The term still ensures the complementarity of charging and discharging operations during a particular time \cite{Nazir2021Sep}.

% \begin{equation}
%     \min {\sum_{t = 1}^{T} \left[ C^t P^t_{Subs} + \alpha \sum_{j \in \mathcal{B}} \left\{ (1-\eta_C)P^t_{C_j} + \left( \frac{1}{\eta_D} - 1 \right) P^t_{D_j}\right\} \right] } \label{eq:genCost_withSCD}
% \end{equation}
\begin{equation}
    \begin{split}
        \min \sum_{t = 1}^{T} \left[ C^t P^t_{Subs} \Delta t+ \alpha \sum_{j \in \mathcal{B}} \left\{ (1-\eta_C)P^t_{C_j} \right. \right. \\
        \left. \left. + \left( \frac{1}{\eta_D} - 1 \right) P^t_{D_j} \right\} \right]
    \end{split}
    \label{eq:genCost_withSCD}
\end{equation}


Subject to the constraints \crefrange{eq:RealPowerBalanceNodej}{eq:modelEndsHere-and-lim_Bj} as given below:

\begin{align}
    % {p_j^t} & = {\sum_{(j, k) \in \mathcal{L}} P_{jk}^t - \left\{P_{ij}^t - r_{ij}l_{ij}^t\right\} - P_{d_j}^t + P_{c_j}^t} && \label{eq:RealPowerBalanceNodej} \\ 
    % {0} &= {\sum_{(j, k) \in \mathcal{L}} \left\{P_{jk}^t\right\} - \left(P_{ij}^t - r_{ij}l_{ij}^t\right) - \left(P_{d_j}^t - P_{c_j}^t\right) - p^t_{D_j} + p^t_{L_j}} && \label{eq:RealPowerBalanceNodej} \\ 
    % \begin{align}
    {0} &= {\sum_{(j, k) \in \mathcal{L}} \left\{P_{jk}^t\right\} 
        - \left(P_{ij}^t - r_{ij}l_{ij}^t\right)} \nonumber && \\[-0.50em]
    {}  &\qquad \qquad {- \left(P_{d_j}^t - P_{c_j}^t\right) - p^t_{D_j} + p^t_{L_j}}
    \label{eq:RealPowerBalanceNodej} &&
\end{align}

\vspace{-1.5em} % Adjust the space as needed

\begin{align}
% \end{align}
    % \end{align}
    % {q_j^t} & = {\sum_{(j, k) \in \mathcal{L}} Q_{jk}^t - \left\{Q_{ij}^t - x_{ij}l_{ij}^t\right\} - q_{D_j}^t - q_{B_j}^t} && \label{eq:Qij} \\ 
    % {0} &= {\sum_{(j, k) \in \mathcal{L}} \left\{Q_{jk}^t\right\} - \left(Q_{ij}^t - x_{ij}l_{ij}^t\right) - q_{D_j}^t - q_{B_j}^t - q_{C_j} + q^t_{L_j}} && \label{eq:ReactivePowerBalanceNodej} \\ 
    % \begin{align}
    {0} &= {\sum_{(j, k) \in \mathcal{L}} \left\{Q_{jk}^t\right\} 
        - \left(Q_{ij}^t - x_{ij}l_{ij}^t\right)} \nonumber && \\[-0.50em]
    {} & \qquad \qquad { - q_{D_j}^t - q_{B_j}^t + q^t_{L_j} }
    % - q_{C_j}  
    % \label{eq:ReactivePowerBalanceNodej} && \\[0.75em]
    \label{eq:ReactivePowerBalanceNodej} &&
\end{align}
    % \end{align}
    % {p_j^t} &= {p_D{_j}^t - p_L{_j}^t} \label{eq:pj}\\
    % {q_j^t} &= {q_C{_j} -q_L{_j}^t} \label{eq:qj}\\
    % {v_j^t} & = {v_{i}^t +  \left\{r_{ij}^2 + x_{ij}^2\right\}l_{ij}^t - 2(r_{ij}P_{ij}^t + x_{ij}Q_{ij}^t)} \label{eq:vj} && \\
    % {0} &= {v_{i}^t - v_j^t - 2(r_{ij}P_{ij}^t + x_{ij}Q_{ij}^t) + \left\{r_{ij}^2 + x_{ij}^2\right\}l_{ij}^t} \label{eq:KVL-branch-ij} && \\

\vspace{-1.5em} % Adjust the space as needed

\begin{equation}
    {0} = {v_{i}^t - v_j^t - 2(r_{ij}P_{ij}^t + x_{ij}Q_{ij}^t) + \left\{r_{ij}^2 + x_{ij}^2\right\}l_{ij}^t} \label{eq:KVL-branch-ij}
\end{equation}


% \begin{align}
%     {0} &= {v_{i}^t - v_j^t - 2(r_{ij}P_{ij}^t + x_{ij}Q_{ij}^t)} \nonumber && \\[-0.00em]
%     {} &\qquad \qquad {+ \left\{r_{ij}^2 + x_{ij}^2\right\}l_{ij}^t} \label{eq:KVL-branch-ij} &&
% \end{align}

\vspace{-1.5em} % Adjust the space as needed

\begin{align}
    % {l_{ij}^t} & = {\frac{(P_{ij}^{t})^2 + (Q_{ij}^{t})^2}{v_i^t}} \label{eq:lij} && \\
    {0} &= {(P_{ij}^{t})^2 + (Q_{ij}^{t})^2 - l_{ij}^t v_i^t} \label{eq:ApparentPowerEquationBFM} &&
\end{align}

\vspace{-1.5em} % Adjust the space as needed

\begin{align}
    {P^t_{Subs}} &\geq {0} \label{eq:substationRealPowerLimits} &&
\end{align}

\vspace{-1.5em} % Adjust the space as needed

% \begin{align}
%     { l^{t}_{ij} } &\in { \left[ 0, I^{2}_{R, ij}
%     \right] } \label{eq:lim_lij} &&
% \end{align}

% \vspace{-1.5em} % Adjust the space as needed

\begin{align}
    { v^{t}_{j} } &\in { \left[ V^{2}_{min}, V^{2}_{max} \right]} \label{eq:lim_vj} &&
\end{align}

\vspace{-1.5em} % Adjust the space as needed

\begin{align}
    { q^{t}_{D_{j}} } 
    &\in
    { \left[-\sqrt{ {S_{D_{R, j}}}^2 - {p^{t}_{D_{j}}}^2}, \sqrt{ {S_{D_{R, j}}}^2 - {p^{t}_{D_{j}}}^2}\right] } \label{eq:qDj} &&
\end{align}

\vspace{-1.5em} % Adjust the space as needed

\begin{align}
    {0} &= {  B_{j}^{t} - \left\{B_{j}^{t-1} + \Delta t  \eta_c P_{c_j}^t - \Delta t\frac{1}{\eta_d} P_{d_j}^t \right\} } \label{eq:SOC-j} &&
\end{align}

\vspace{-1.5em} % Adjust the space as needed

\begin{align}
    { P^{t}_{c_{j}}, P^{t}_{d_{j}} }
    &\in
    { \left[ 0, P_{B_{R_{j}}} \right]}, \quad B_{j}^{0}=B_{j}^{T} \label{eq:lim_PcPdj} &&
\end{align}

\vspace{-1.5em} % Adjust the space as needed

\begin{align}
    % { q^{t}_{B_{j}} } 
    % &\in 
    % { \left[-\sqrt{ {S_{B_{R, j}}}^2 - {P_{B_{R, j}}}^2}, \sqrt{ {S_{B_{R, j}}}^2 - {P_{B_{R, j}}}^2}\right] } \label{eq:qBj} && \\
    { q^{t}_{B_{j}} } 
    &\in 
    { \left[-0.44P_{B_{R, j}}, 0.44P_{B_{R, j}}\right] } \label{eq:qBj} &&
\end{align}

\vspace{-1.5em} % Adjust the space as needed

\begin{align}
    % { B^{t}_{j} } &\in { \left[ soc_{min}B_{R, j}, soc_{max}B_{R, j} \right] } \label{eq:lim_Bj} && \\
    { B^{t}_{j} } &\in { \left[ soc_{min}B_{R, j}, soc_{max}B_{R, j} \right] } \label{eq:modelEndsHere-and-lim_Bj} &&
    % {} & {} \nonumber \label{eq:modelEndsHere-and-lim_Bj}
\end{align}

The distribution network is represented with the help of the branch power flow equations \crefrange{eq:RealPowerBalanceNodej}{eq:ApparentPowerEquationBFM}. Constraints \cref{eq:RealPowerBalanceNodej,eq:ReactivePowerBalanceNodej} signify the active and reactive power balance at node $j$, respectively
% including contributions from any attached DERs ($p^t_{D_j} , q^t_{D_j}$) and/or batteries ($P^t_{c_j}, P^t_{d_j}, q^t_{B_j}$). 
% The net active and reactive power injections at any bus \(j\) are represented by \cref{eq:pj,eq:qj} respectively. 
The KVL equation for branch $(ij)$ is represented by \cref{eq:KVL-branch-ij}, while the equation describing the relationship between current magnitude, voltage magnitude and apparent power magnitude for branch $(ij)$ is \cref{eq:ApparentPowerEquationBFM}. Backflow of real power into the substation from the distribution system is avoided using the constraint \cref{eq:substationRealPowerLimits}. The box limits for squared node voltage are enforced via \cref{eq:lim_vj}. \cref{eq:qDj} describes the reactive power limits of DER inverters. The trajectory of the battery energy versus time is given by \cref{eq:SOC-j} and is the only time-coupled constraint in this paper. Battery charging and discharging powers are limited by the battery's rated power capacity, as given by \cref{eq:lim_PcPdj}. \cref{eq:lim_PcPdj} also says that the initial and final energy levels must be the same. Every battery's reactive power is also constrained based on the associated inverter's rated capacity, as described by \cref{eq:qBj}. For the safe and sustainable operation of the batteries, the energy $B^{t}_{j}$ is constrained to be within some percentage limits of the rated battery soc capacity, as given in \cref{eq:modelEndsHere-and-lim_Bj}

% Node $i$ denotes the `parent' node of node $j$, which itself may be the parent of a set of $k$ `children' nodes (the set may contain one, many or even zero nodes, if $j$ is a leaf node). It may be noted that for a radial distribution system, each node $j$ can have only one `parent' node $i$.


\subsection{ENApp based MPDOPF with Batteries} \label{subsec:ENApp}
Assuming the presence of a feasible solution for the MPCOPF problem, the MPDOPF is formulated by decomposing the bulk distribution grid into multiple small areas. In this paper, the interaction between the two areas will follow the principle of ENApp algorithm. The ENApp algorithm leverages the radial topology of the distribution network. Each area has a local controller (LC) that solves its specific local optimization problem by enabling boundary value sharing with neighboring areas. The local optimization problem will be the same MPOPF one described in Section II-B but only with the variables and parameters for that area. Common boundary buses between two areas are accounted as voltage sources for downstream areas and load buses for upstream areas. Now by knowing the upstream voltage and downstream load data, the LCs will solve its area-specific MPOPF in parallel. After that, the downstream and upstream LCs inform power flows and voltage data to their respective upstream and downstream areas, respectively. The LCs will again solve their local MPOPF and interchange updated boundary information. This iterative process terminates only if consensus is reached at all boundary buses. Detailed ENApp algorithm can be found in \cite{Sadnan}.

For $T$ number of time steps, any area shares a data vector of $2T$ boundary variables with its neighbors. Among $2T$, both voltage and power data are of size $T$. Therefore, if total number of areas is $A$, then the total number of area interconnections is $A-1$. Hence, simultaneously $2(A-1)T$ number of boundary variables will be shared at each iteration.

% Solving a nonlinear nonconvex OPF problem is computationally intensive. In the ENApp paradigm, the original OPF problem is divided into several subproblems, based on physically connected `parent-child' area relationships in the radial distribution network. ENApp primiarly requires three classes of operations. The first is of course solving for the OPF of each individual subproblem, the second is checking for `boundary convergence' between related areas to check if further improvement iterations are needed and the third and last operation is exchange of variables between related areas for subsequent iterations. Out of these three operations, only solving the OPF is computationally intensive. 

% The key advantage of using ENApp in preference to MPCOPF is its efficient division of the OPF problem into several smaller problems via efficient exploitation of power flow physics in a radial network \cite{Sadnan}. Typically, Nonlinear Programming problems grow superlinearly in complexity with increase in problem size, and thus division of the OPF problem into smaller, more manageable chunks greatly speeds up the solution process.

% The solution process for each subproblem can then be parallelized, saving computation time even further.

% Additionally, on paper it might appear that ENApp requires solving of the subproblems across multiple iterations, potentially nullifying the benefit from reduction in problem size. However in practice, once the first OPF iteration is completed for each area, the results can be used to `warm-start' subsequent iterations with significant speedups in solution times.

% Thus, in essence, the `computational bottleneck' for ENApp is computing the OPF solution of its biggest subproblem, which typically translates to the single biggest area as part of the spatial decomposition of the radial distribution grid (assuming the number of DERs and Batteries is not significantly higher in another area).

% The advantage of this smaller computational bottleneck will be readily seen in \Cref{subsec:simulationResults,subsec:scalabilityAnalysis} when compared against MPCOPF on the Test System. 

% For the rest of this paper, we'll be addressing ENAPpp based Distributed Multi-Period OPF simply as MPDOPF for brevity.

\end{document}
